---
title: "bst216_05asses"
author: "Keiko"
date: "9/18/2019"
output: html_document
---
1. Compute the per 100,000 murder rate for each state and store it in an object called murder_rate. Then use the logical operators to create a logical vector, name it low, that tells us which entries of murder_rate are lower than 1.
```{r}
murders$murder_rate<-murders$total/murders$population *100000
low<- murders$murder_rate<1 
low
```

2. Now use the results from the previous exercise and the function which to determine the indices of murder_rate associated with values lower than 1.
```{r}
ind<- which(murders$murder_rate<1) 
```


3. Use the results from the previous exercise to report the names of the states with murder rates lower than 1.
```{r}
murders$state[ind]
```

4. Now extend the code from exercises 2 and 3 to report the states in the Northeast with murder rates lower than 1. Hint: Use the previously defined logical vector low and the logical operator &.
```{r}
NE<-murders$region=="Northeast"
NE
murders$state[low&NE]
```

5. In a previous exercise we computed the murder rate for each state and the average of these numbers. How many states are below the average?
```{r}
mean(murders$murder_rate)
low_ave<-murders$murder_rate<2.779125
sum(low_ave)
```

```{r}
avg<-mean(murders$murder_rate)
sum(murders$murder_rate<avg)
```

6. Use the match function to identify the states with abbreviations AK, MI, and IA. Hint: Start by defining an index of the entries of murders$abb that match the three abbreviations, then use the [] operator to extract the states.
```{r}
ind<- match(c("AK","MI","IA"),murders$abb)
murders$state[ind]
```

7. Use the %in% operator to create a logical vector that answers the question: which of the following are actual abbreviations: MA, ME, MI, MO, MU?
```{r}
c("MA","ME","MI","MO","MU") %in% murders$abb 
```
```{r}
ind<-which(c("MA","ME","MI","MO","MU") %in% murders$abb) 
ind
murders$state[ind]
```

8. Extend the code you used in exercise 7 to report the one entry that is not an actual abbreviation. Hint: Use the ! operator, which stands for “not” and turns FALSE into TRUE and vice-versa, then which to obtain an index.
```{r}
ind2<-which(c("MA","ME","MI","MO","MU") %in% murders$abb != TRUE)
ind2
```