---
title: "BST260lecture_memo"
author: "Keiko"
date: "9/11/2019"
output: html_document
---
## 20190911
#### to update the repository
Open Git


==

cd Desktop

cd 2019

git pull

==

#### lecture memo190911
add r, cache=TRUE, eval=FALSE
```{r, cache=TRUE, eval=FALSE}
a <- 2
class(a)
```

add r, cache=FALSE, eval=TRUE
```{r, cache=FALSE, eval=TRUE}
a <- 2
class(a)
```


== is equal to, = is assigning (similar to <-) 


### 190916
##### order

order shows us how to change the original order to make it ordered
```{r}
x<-c( 31,4,15,92,65)
x
order(x)
```

If you want to make it descending order,
```{r}
order(x, decreasing=TRUE)
```

#####rank
```{r}
rank(x)
```



see max
```{r}
murders$state[which.max(murders$total)]
```
instead of

*i_max<-which.max(murders$total)

murders$state[i_max]*

##### ex. usage of order
```{r}
library(dslabs)
data(murders)
sort(murders$total)

ind <- order(murders$total) 
ind
murders$abb[ind] 
```

we can combine provided codes
```{r}
murders$state[which.max(murders$total)]
```

wecan also calculate and sort like this
```{r}
murder_rate<-murders$total /murders$population *10000
murder_rate
murders$abb[order(murder_rate)]
```

to see the murder rate of Ca
```{r}
murder_rate[which(murders$state=="California")]
```

to see some states
```{r}
murder_rate[]
```

### 190918

#### how to use !
```{r}
ind2<-which(c("MA","ME","MI","MO","MU") %in% murders$abb != TRUE)
ind2
```

#### Summarize

The `summarize` function in `dplyr` provides a way to compute summary statistics with intuitive and readable code. We can compute the average of the murder rates like this.


```{r}
murders %>% summarize(avg = mean(murder_rate))
```
output is in "data.frame"

weighted average can calculated with summarize
```{r}
us_murder_rate <- murders %>% 
  summarize(murder_rate = sum(total) / sum(population) * 100000)

us_murder_rate
```

to obtain actual number itself, use this
```{r}
us_murder_rate %>% .$murder_rate
```